A scenario for a Planckian standard kilogram

### 2017-10-31 manuscript_gravitationalconstant.tex
spelling errors corrected
conclusion edited

In the next step, we set the parameters to a fixed ``true" value
within the range estimated. We have to keep in mind that $k$, $x_0$
and $v_{y_0}$ are linked together and there must not be contradictions
in the true values. The chosen values are displayed in the right
column in Table~\ref{tab:parameters}.  To simulate data we would
obtain from the position measurements, we integrate the equations of
motion. The time for one orbit without perturbations can be estimated
using Kepler's third law (\ref{eq:kepler3}). For the value of $k$
assumed above and a semi-major axis of $0.15 \, \mathrm{m}$, this
results in an orbital period of roughly $12900 \, \mathrm{seconds}$ or
$3.5 \, \mathrm{hours}$. Here we integrate two orbits in $100000$
steps, that would correspond to about $4$ measurements per second,
which should be feasible. To the generated data, we add Gaussian noise
with a standard deviation of $10 \, \mathrm{nm}$. This uncertainty
stays for a systematic error in the laser interferometry measurement
and also random statistic noise. The value we use is just an estimate,
it would depend strongly on the measurement system that has been used.

@@

\section{Conclusion}
We have outlined an orbit experiment to measure the gravitational
constant $G$, and estimated the level of various disturbing effects
and how to correct for them.  Simulating the measurement process and
extraction of the gravitational constant indicates that $G$ could be
estimated to about $10^{-7}$ relative uncertainty.  This is a about a
factor of 300 better than today's recommended CODATA value.  If we are
a bit optimistic, a further increase in precision is not out of reach,
so that about the same relative uncertainty as for Planck's constant
$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved. This then
would allow a future redefination of the kilogram as an integer
multiple of the Planck mass.

>>>>

In the next step, we set the parameters to a fixed ``true" value
within the range estimated. We have to keep in mind that $k$, $x_0$
and $v_{y_0}$ are linked together and there must not be contradictions
in the true values. The chosen values are displayed in the right
column in Table~\ref{tab:parameters}.  To simulate data we would
obtain from the position measurements, we integrate the equations of
motion. The time for one orbit without perturbations can be estimated
using Kepler's third law (\ref{eq:kepler3}). For the value of $k$
assumed above and a semi-major axis of $0.15$~m, this
results in an orbital period of roughly 12900 seconds or
3.5 hours. Here we integrate two orbits in 100000
steps, that would correspond to about 4 measurements per second,
which should be feasible. To the generated data, we add Gaussian noise
with a standard deviation of 10~nm. The value we use is just an estimate,
it would depend strongly on the measurement system that has been used.

@@

\section{Conclusion}
We have outlined an orbit experiment to measure the gravitational
constant $G$, and estimated the level of various disturbing effects
and how to correct for them.  Simulating the measurement process and
extraction of the gravitational constant indicates that $G$ could be
estimated to about $10^{-7}$ relative uncertainty.  This is a about a
factor of 300 better than today's recommended CODATA value. A further increase in precision could be obtained by running the experiment longer. Measuring for 200 instead of two orbits could increase the precision by a factor of 10.
Hence, about the same relative uncertainty as for Planck's constant
$h$ ($1.2 \cdot 10^{-8}$)\cite{CODATA16} could be achieved. This then
would allow a future redefinition of the kilogram as an integer
multiple of the Planck mass.

We are not supposing the measurement of the gravitational constant 
using an artificial two-body system at an Earth-Sun Lagrange point to be a stand alone mission. It could just be part of 
a spacecraft reaching a Lagrange point. But our estimates suggest that this approach to increase the precision of the gravitational constant should be taken seriously.
